---
title: "ETM 58D FINAL"
author: "Sena Torlak"
date: "`r Sys.Date()`"
output: html_document
---
#Finding Datasets

Here is my data sets withing their explanations about attributes and aims. 

<ol>
<li><a href="https://archive.ics.uci.edu/ml/datasets/Online+News+Popularity">Online News Popularity</a></li>

<li><a href="http://archive.ics.uci.edu/ml/datasets/Absenteeism+at+work#">Absenteeism at Work</a></li>


<li><a href="http://archive.ics.uci.edu/ml/datasets/Dry+Bean+Dataset#">Dry Bean</a></li>

</ol>

#Online News Popularity 

This dataset provides information about different websites traffics with various details including popularity,shares and sentiment analyses.

```{r setup, include=FALSE}
install.packages("rpart")
install.packages('rpart.plot')
install.packages('caret')
install.packages('rattle')
install.packages('randomForest')
install.packages('ranger')
install.packages('openxlsx')
install.packages('data.table')
install.packages('skimr')
install.packages(file.choose(),repos=NULL)
install.packages("readxl")

require(ggplot2)
require(tidyverse)
require(rpart)
require(dplyr)
require(rpart.plot)
require(caret)
require(rattle)
require(randomForest)
require(ranger)
require(openxlsx)
require(readxl)
require(skimr)
require(data.table)

data_path_onlinenews=file.choose()
onlinenews=read_excel(data_path_onlinenews,sheet=1)
str(onlinenews)

summary_data_onlinenews=skim(onlinenews)
print(summary_data_onlinenews)

onlinenews=data.table(onlinenews)
str(onlinenews)
```

##Analysis

Since the dependent variables of the dataset is shares, I would like to choose that coloumn.

```{r setup, include=FALSE}
install.packages("caTools")
library(caTools)

set.seed(1234)

sample_onlinenews <- sample.split(onlinenews$shares, SplitRatio = 0.7)
train_onlinenews  <- subset(onlinenews, sample_onlinenews == TRUE)
test_onlinenews   <- subset(onlinenews, sample_onlinenews == FALSE)

head(train_onlinenews)
head(test_onlinenews)

```
###Decision Tree

```{r setup, include=FALSE}
library(rpart)

dt <- rpart(shares ~ .,data= train_onlinenews)
rpart.plot(dt, type = 2, box.palette = "Blues")

dt1 <- rpart(shares ~ .,data= train_onlinenews, method= "class")
rpart.plot(dt1, type = 2, extra=5, box.palette = "Blues")
  
predictdata_onlinenews <- predict(dt1,test_onlinenews, type="class")
predictdata_onlinenews
  
table_onlinenews <- table(test_onlinenews$shares, predictdata_onlinenews)
table_onlinenews
  
accuracy_test_onlinenews <- sum(diag(table_onlinenews)) / sum(table_onlinenews)
print(paste('Accuracy for decision tree algorithm', accuracy_test_onlinenews))
  
```


 rf1 <- randomForest(formula= G3 ~ ., data = traindata1, ntree= 500, nodesize =5)
  rf1
  
   which.min(rf1$mse)

